A Taxonomy of Software Product Line Analyses

### 2017-12-09 doc/vamos18/taxonomy.tex
taxonomy outline

\documentclass[sigplan]{acmart}

@@

\author{Ramy Shahin}
\affiliation{%
  \institution{University of Toronto}
}
\email{ramy.shahin@cs.toronto.edu}

\author{Marsha Chechik}
\affiliation{%
  \institution{University of Toronto}
}
\email{marsha.chechik@cs.toronto.edu}

@@

\section{Motivation}
Product line analyses have been surveyed and classified according to different criteria (e.g., \cite{Thum}). 
Modularity of analyses directly impacts the degree of variability the analysis needs to deal with. Since presence conditions are propositional formulas, propositional reasoning is an essential part of any Product Line analysis. The number of propositional variables (which reflects the degree of variability) in formulas is an important factor when it comes to picking the propositional reasoning component used in the analysis. For example, with hundreds or thousands of variables, SAT solvers are usually used. On the other hand, if the number of variables is much lower (10-20), Binary Decision Digarams (BDDs) tend to perform much better. The difference between both reasoning techniques was demonstrated in the difference in performance between Typechef \cite{Kastner} and SuperC \cite{Gazzillo}.

@@

\item A product-level analysis can be used as a white box. Some automatic technique is used to lift the implementation of the product-level analysis into a Produt Line analysis. Since this process is automated, we still consider this approach modular.
\end{itemize}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | l | l |}
\hline
	& Modular & Monolithic \\ \hline
Derived & Hello & World \\ \hline
Rewritten & Hello & World \\ \hline
\end{tabular}
\end{center}
\caption{A taxonomy of Software Product Line analyses}
\label{table:taxonomy}
\end{table}

@@

@@

@@

@@

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{taxonomy} 
\end{document}

>>>>

\documentclass[11pt, english]{article}
\usepackage{babel}

@@

\author{Ramy Shahin \\
  University of Toronto \\
 ramy.shahin@cs.toronto.edu
 \and
  Marsha Chechik \\
  University of Toronto \\
 marsha.chechik@cs.toronto.edu}

@@

\section{Motivation}
Product line analyses have been surveyed and classified according to different criteria (e.g., \cite{Thum:2014}). 
Modularity of analyses directly impacts the degree of variability the analysis needs to deal with. Since presence conditions are propositional formulas, propositional reasoning is an essential part of any Product Line analysis. The number of propositional variables (which reflects the degree of variability) in formulas is an important factor when it comes to picking the propositional reasoning component used in the analysis. For example, with hundreds or thousands of variables, SAT solvers are usually used. On the other hand, if the number of variables is much lower (10-20), Binary Decision Diagrams (BDDs) tend to perform much better. The difference between both reasoning techniques was demonstrated in the difference in performance between Typechef \cite{Kastner:2011} and SuperC \cite{Gazzillo:2012}.

@@

\item A product-level analysis can be used as a white box. Some automatic technique is used to lift the implementation of the product-level analysis into a Product Line analysis. Since this process is automated, we still consider this approach modular.
\end{itemize}

@@

\begin{table*}[t]
\begin{center}
\begin{tabular}{| l | l | l |}
\hline
	& Modular & Monolithic \\ \hline
	Derived & 
		SPL\textsuperscript{LIFT} \cite{Bodden:2013} & 
		FTS \cite{Classen:2010} \\ \hline
	Rewritten & 
		\begin{tabular}{@{}c@{}}
			TypeChef \cite{Kastner:2011} \\ 
			SuperC \cite{Gazzillo:2012}
		\end{tabular} &
			Model Transformations \cite{Salay:2014} \\ \hline
\end{tabular}
\end{center}
\caption{A taxonomy of Software Product Line analyses}
\label{table:taxonomy}
\end{table*}

@@

\subsubsection{SPL\textsuperscript{LIFT}}

@@

\subsubsection{Feature Transition Systems}

@@

\subsubsection{TypeChef}

\subsubsection{SuperC}

@@

\subsubsection{Model Transformations}

@@

\bibliographystyle{abbrv}
\bibliography{taxonomy} 
\end{document}
